---
title: "combiningdbs"
author: "Thomas Van Hoey"
date: "3/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(reticulate)
library(xlsx)
```


# Goals

Combine the following database spreadsheets

* onomatopoeia (based on Li, Gong, Wang)
* full database (mostly based on Kroll)
* Tang shi san bai shou
* Shijing

Pro: we can add many more in the future

# Read in these databases

```{r}
onom <- read_csv("onomatopoeiadb.csv")
# full <- read_csv("Kroll.csv")
full <- read_excel("fulldatabase_onomgreen.xlsx")
tang <- read_csv("300.csv")
shijing <- read_csv("Shijing.csv")

# the partial kroll ones as well for 

```

# Add datasource to every file + select relevant columns

`onom` already ok.
```{r}
onomds <- onom
```

```{r tangds}
# tang
tangds <- tang %>%
  select(`mim simpl`, `mim trad`, `HIERARCHIE DINGEMANSE`,
         #`Gloss meaning`,
         Morf,
         pinyin) %>%
  rename(simplified = `mim simpl`,
         traditional = `mim trad`,
         sensorymod = `HIERARCHIE DINGEMANSE`,
         morphology = Morf,
         pyoriginal = pinyin
         ) %>%
  distinct() %>%
  mutate(datasource = "Tang")
```

```{r full}
fullds <- full %>%
  mutate(datasource = case_when(
    Kroll == "NA" ~ "NA",
    Kroll != "NA" ~ "Kroll"
  )) 
```

```{r shijing}
shijingds <- shijing %>% 
  select(TRAD, SIMPL, PINYIN, SEMANTIC, `FORM-MECH`) %>%
  rename(simplified = SIMPL,
         traditional = TRAD,
         pyoriginal = PINYIN,
         sensorymod = SEMANTIC,
         morphology = `FORM-MECH`) %>%
  mutate(datasource = "Shijing")
```

# Adding pinyin 
`onomds`, `fullds` are okay in this respect
`tangds`, `shijingds` need to be checked

## Tangds pinyin

```{r}
file <- tangds
```

load in
```{r pythonreticulate}
use_python("/usr/local/bin/python3", required = T)
reticulate::py_config()
```

get only the characters from our list
```{r unlisting}
list <- file %>%
  select(traditional) %>%
  unlist()
```


```{python pyscript}
import pinyin
a = r.list

richard = []
for i in a:
    richard.append(i)

thomas = []
for i in a:
    j = pinyin.get(i, delimiter="~")
    thomas.append(j)
    
cj = []
for i in a:
    j = pinyin.get(i, format= "strip", delimiter="~")
    cj.append(j)
    
arthur = []
for i in a:
    j = pinyin.get(i, format="numerical", delimiter="~")
    arthur.append(j)
#print (thomas)
#print(type(thomas))
```

```{r pythonvars}
#py_run_file("script.py")
#py_run_string("x = 10")

# access the python main module via the 'py' object
#py$x
thomas <- py$thomas #%>% tibble()
thomas <- tibble(thomas)

cj <- py$cj #%>% tibble()
cj <- tibble(cj)

arthur <- py$arthur #%>% tibble()
arthur <- tibble(arthur)

#thomas
#cj
#arthur
```

```{r joiningnewpinyin, cache=TRUE}
tangpy <- cbind(file, arthur, thomas, cj) %>%
  rename(pinyinnum = arthur,
         pinyintone = thomas,
         pinyinnone = cj, 
         traditional  = traditional)
```

## Shijingds pinyin

```{r}
file <- shijingds
```

load in
```{r pythonreticulate}
use_python("/usr/local/bin/python3", required = T)
reticulate::py_config()
```

get only the characters from our list
```{r unlisting}
list <- file %>%
  select(traditional) %>%
  unlist()
```


```{python pyscript}
import pinyin
a = r.list

richard = []
for i in a:
    richard.append(i)

thomas = []
for i in a:
    j = pinyin.get(i, delimiter="~")
    thomas.append(j)
    
cj = []
for i in a:
    j = pinyin.get(i, format= "strip", delimiter="~")
    cj.append(j)
    
arthur = []
for i in a:
    j = pinyin.get(i, format="numerical", delimiter="~")
    arthur.append(j)
#print (thomas)
#print(type(thomas))
```

```{r pythonvars}
#py_run_file("script.py")
#py_run_string("x = 10")

# access the python main module via the 'py' object
#py$x
thomas <- py$thomas #%>% tibble()
thomas <- tibble(thomas)

cj <- py$cj #%>% tibble()
cj <- tibble(cj)

arthur <- py$arthur #%>% tibble()
arthur <- tibble(arthur)

#thomas
#cj
#arthur
```

```{r joiningnewpinyin, cache=TRUE}
shijingpy <- cbind(file, arthur, thomas, cj) %>%
  rename(pinyinnum = arthur,
         pinyintone = thomas,
         pinyinnone = cj, 
         traditional  = traditional)
shijingpy
```

```{r}
names(shijingpy)
names(tangpy)
```

```{r}
tangpy <- tangpy %>%
  select(traditional, simplified, 
         pyoriginal, pinyintone, pinyinnum,
         morphology,
         sensorymod,
         datasource)

shijingpy <- shijingpy %>%
  select(traditional, simplified, 
         pyoriginal, pinyintone, pinyinnum,
         morphology,
         sensorymod,
         datasource)

full_join(tangpy, shijingpy) %>%
  mutate(inbetween = str_replace(pinyintone,"~", "")) %>%
  mutate(same = case_when(
    pyoriginal == inbetween ~ "same",
    pyoriginal != inbetween ~ "different"
  )) %>%
  write_csv("tang_shijing_pinyin.csv", col_names = TRUE)
```

This file has been checked for erroneous pinyin generation
```{r}
shijingtangpy <- read_csv("tang_shijing_pinyin_checked.csv") %>%
  distinct() %>%
  select(-inbetween, -same, -pyoriginal) %>%
  mutate(pinyinnone = str_replace_all(pinyinnum, "[12345]", ""))
shijingtangpy
```

# Middle Chinese and Old Chinese

`onomds`, `fullds` are okay in this respect
`shijingtangpy` needs to be checked

```{r}
splitcharacters <- shijingtangpy %>%
  mutate(c1 = str_extract(traditional, "^."),
         c2 = str_extract(traditional, "^.."),
         c3 = str_extract(traditional, "^...")
         ) %>%
  mutate(c2 = str_replace(c2, "^.", ""),
         c3 = str_replace(c3, "^..", ""))
splitcharacters
```

load in Baxter Sagart

```{r}
baxter <- readxl::read_excel("../BaxterSagartOC2015-10-13.xlsx") %>%
  rename("middle" = "MC", "old" = "OC") %>%
  select(zi, middle, old)
head(baxter)
```

```{r}
midandoldpercharacter <- splitcharacters %>% 
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c1"= "zi")) %>%
  rename("m1" = "middle",
         "o1" = "old") %>% # this lef_join and rename function gets repeated but the number is changed
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c2"= "zi")) %>%
  rename("m2" = "middle",
         "o2" = "old") %>%
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c3"= "zi")) %>%
  rename("m3" = "middle",
         "o3" = "old") 

# combinations
nummers <- 1:3
middles <- paste0("m", nummers)
olds <- paste0("o", nummers)

tangshijingMO <- midandoldpercharacter %>%
  unite(middles, col = "MC", sep = "~") %>%
  unite(olds, col = "OC", sep = "~") %>%
  mutate(OC = str_replace(OC, "NA~NA~NA", "NA"),
         OC = str_replace(OC, "~NA$", ""),
         MC = str_replace(MC, "NA~NA~NA", "NA"),
         MC = str_replace(MC, "~NA$", "")
         )
tangshijingMO
```

# Joining

```{r}
joinedtable <- full_join(fullds, tangshijingMO)
joinedtable
```

Do the ones that occur with NA for datasource occur minimally in Shijing or Tang? If so, they probably came from there and can be changed in Shijing and/or Tang

As the anti_join shows, there are no rows that do not occur already elsewhere in the table.
So they can be safely dropped.

```{r}
joinedtable %>%
  group_by(datasource) %>%
  tally()

anti <- joinedtable %>%
  filter(datasource == "NA") %>%
  select(traditional)

anti %>%
  anti_join(joinedtable, by = c("traditional" = "traditional"))

```

```{r}
joineddropsourcena <- joinedtable %>%
  filter(datasource != "NA")
# joineddropsourcena
```

Let's add the onomatopoeia

```{r}
finaltable <- joineddropsourcena %>%
  full_join(onomds) %>%
  select(-c1, -c2, -c3) %>%
  distinct()
```


# Write output

```{r}
# write.xlsx(finaltable, "combinedtable.xlsx", col.names = TRUE, showNA = FALSE)

finaltable

# write_csv(finaltable, "combinedtable.csv", col_names = TRUE)

finaltable %>%
  group_by(morph) %>%
  tally()

# taking the non-ideophones out
finaltable %>%
  filter(morph == 'NOTIDEOPHONE') %>%
  write_csv("notideophones.csv", col_names = TRUE)

finaltable <- finaltable %>%
  filter(morph != 'NOTIDEOPHONE' | is.na(morph))

write_csv(finaltable, "combinedtable.csv", col_names = TRUE)

finaltable
```




# Aftercare

check modality in the new database
(esp. in Kroll)

# Statistics

```{r}
syllength <- 
  finaltable %>%
  select(traditional) %>%
  mutate(length = nchar(traditional)) %>%
  group_by(length) %>%
  count() %>%
  filter(length != "5" & length != "6")# %>%


  
syl.chi <- syllength %>%
  ungroup() %>%
  mutate(expected = sum(n)/4)

syl.chi

as.table(syl.chi$expected, syl.chi$n)

chisq.test(syllength$n, p = c(0.25, 0.25, 0.25, 0.25))

syllength

``` 



