---
title: "Terminology ideophones"
author: "Thomas Van Hoey"
date: "9/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lingtypology)
```

Goal: to create a map that shows which for which languages we use which terminology relating to ideophones.


```{r}
country.lang("Dutch")
```


```{r}
df <- read_csv("https://raw.githubusercontent.com/simazhi/ideophones/master/terminology_map.csv")
df
```




```{r}
map.feature(languages = df$language,
            features = df$terminology,
            popup = df$popup,
            #color= c("yellowgreen", "navy"),
            #shape = TRUE
            label = df$language
            )

```






# References



Dingemanse, Mark. 2011. The meaning and use of ideophones in Siwu. Nijmegen: Radboud University Nijmegen dissertation.


Kwon, Nahyun. 2015. The natural motivation of sound symbolism. Brisbane: University of Queensland PhD dissertation.


Moroz G (2017). _lingtypology: easy mapping for Linguistic Typology_. <URL: https://CRAN.R-project.org/package=lingtypology>.

Voeltz, Erhard Friedrich Karl & Christa Kilian-Hatz (eds.). 2001. Ideophones. (Typological Studies in Language v. 44). Amsterdam ; Philadelphia: J. Benjamins.

