---
title: "Terminology ideophones"
author: "Thomas Van Hoey"
date: "9/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lingtypology)
```

Goal: to create a map that shows which for which languages we use which terminology relating to ideophones.


```{r}
country.lang("Dutch")
```





# Making a table with all the languages, terminology and bibliography
```{r}
#first put in all the languages
#it is best to add a language and its bibliography together
languages <- c("Semai_expressive",
               "Bahnar_expressive",
               "Kedah Malay_expressive",
               "Lao_expressive",
               "Indonesian_expressive",
               "Somali_ideophone",
               "Yoruba_ideophone",
               "Kisi_ideophone",
               "Zulu_ideophone",
               "Gbaya-Bossangoa_ideophone",
               "Hausa_ideophone",
               "Siwu_ideophone",
               "Korean_ideophone",
               "Asheninka Perene_ideophone",
               "Japanese_mimetic",
               "French_expressive",
               "Northern Pastaza Quichua_ideophone"
               )

#adding the bibliography + the terms used in that language (if we know)
# this can be formatted using html
bibliography <- c("Diffloth (1976); Tufvesson (2011)",
                  "Diffloth (1994)",
                  "Collins (1979)",
                  "Crisfield (1983); Wayland (1996)",
                  "Carr (1966)",
                  "Dhoorre & Tosco (1998)",
                  "Rowlands (1970)",
                  "Childs (1988)",
                  "Doke 1935",
                  "Samarin (1965)",
                  "Newman (1968)",
                  "Dingemanse (2011)",
                  "Lee (1992)",
                  "Mihas (2012)",
                  "Lu (2006); Akita (2009); Kita (1997); Mester & Itô (1989), Rodrigues (1604) <br>
                  オノマトペ・擬音語・擬態語・擬情語",
                  "Grammont (1901)",
                  "Nuckolls (1992; 1996; 2004; 2017)"
                  )

languages

df_pre <- tibble(languages, popup = bibliography)
df_pre



df <- df_pre %>% 
  separate(languages, into = c("language", "terminology"), sep = "_")



df


```




```{r}
map.feature(languages = df$language,
            features = df$terminology,
            popup = df$popup,
            color= c("yellowgreen", "navy"),
            #shape = TRUE
            label = df$language
            )

```






# References



Dingemanse, Mark. 2011. The meaning and use of ideophones in Siwu. Nijmegen: Radboud University Nijmegen dissertation.


Kwon, Nahyun. 2015. The natural motivation of sound symbolism. Brisbane: University of Queensland PhD dissertation.


Moroz G (2017). _lingtypology: easy mapping for Linguistic Typology_. <URL: https://CRAN.R-project.org/package=lingtypology>.

