---
title: "Terminology ideophones"
author: "Thomas Van Hoey"
date: "9/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

#Goal

Goal: to create a map that shows which for which languages we use which terminology relating to ideophones.

# Load packages
```{r}
library(tidyverse)
library(lingtypology)
```


# Read in the data

The data below is divided into three columns:

* `language`: the language name found in the [Glottolog database](http://glottolog.org/)^[Although maybe it is an adapted form, [see the documentation for the R package 'lingtypology'](https://ropensci.github.io/lingtypology/lingtypology_glottolog_functions.html).].
* `terminology`: the terminology used to refer to ideophones in descriptions of the phenomenon across different languages.
* `popup`: What I want to appear in the frames when you click on a given language. In this case that would be a reference to some research, or the names used for the phenomenon in the language itself.

```{r data, warning=FALSE, message=FALSE}
df <- read_tsv("https://raw.githubusercontent.com/simazhi/ideophones/master/terminology_map.csv")
df
```


# Plot the terminology map

Next we plot the map, which can then be explored.

```{r map}
map.feature(languages = df$language,
            features = df$terminology,
            popup = df$popup,
            color= c("yellowgreen", "navy"),
            #shape = TRUE
            label = df$language
            )

```






# References

Dingemanse, Mark. 2011. The meaning and use of ideophones in Siwu. Nijmegen: Radboud University Nijmegen dissertation.

Kwon, Nahyun. 2015. The natural motivation of sound symbolism. Brisbane: University of Queensland PhD dissertation.

Moroz G (2017). _lingtypology: easy mapping for Linguistic Typology_. <URL: https://CRAN.R-project.org/package=lingtypology>.

Voeltz, Erhard Friedrich Karl & Christa Kilian-Hatz (eds.). 2001. Ideophones. (Typological Studies in Language v. 44). Amsterdam ; Philadelphia: J. Benjamins.

