---
title: "Terminology ideophones"
author: "Thomas Van Hoey"
date: "9/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lingtypology)
```

Goal: to create a map that shows which for which languages we use which terminology relating to ideophones.


```{r}
country.lang("Dutch")
```


The term ‘ideophone’ is commonly used to refer to a class of sound-symbolic words in sub-Saharan
African languages, such as Somali (Dhoorre & Tosco, 1998), Yoruba (Rowlands, 1970), Kisi
(Childs, 1988), Zulu (Doke, 1935), Gbeya (Samarin, 1965), Hausa (Newman, 1968), Siwu
(Dingemanse, 2011), and in some other non-African languages, such as Korean (Lee, 1992) and
Alto Perené (Mihas, 2012).


# Making a table with all the languages, terminology and bibliography
```{r}
#first put in all the languages

#it is best to add a language and its bibliography together
languages <- c("Semai_expressive",
               "Bahnar_expressive",
               "Kedah Malay_expressive",
               "Lao_expressive",
               "Indonesian_expressive",
               "Japanese_mimetic"
               )

bibliography <- c("Diffloth (1976); Tufvesson (2011)",
                  "Diffloth (1994)",
                  "Collins (1979)",
                  "Crisfield (1983); Wayland (1996)",
                  "Carr (1966)",
                  "Akita (2009)"
                  )

languages

df_pre <- tibble(languages, popup = bibliography)
df_pre



df <- df_pre %>% 
  separate(languages, into = c("language", "terminology"), sep = "_")



df


```




```{r}
map.feature(languages = df$language,
            features = df$terminology,
            popup = df$popup,
            color= c("yellowgreen", "navy"),
            #shape = TRUE
            label = df$language
            )

```











