---
title: "Let’s build a database"
author: "Thomas Van Hoey"
date: "19/9/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

What I want to do is combine three documents together:
1. My own database project (.odb)
2. Kroll's (2015) A-M (by Arthur)
3. Kroll's (2015) N-Z (by Thomas)

# Package load
```{r}
library(tidyverse)
library(ODB)
library(tmcn)
library(pinyin)
```


# The .odb database

## Getting the R-object and wrangling

First we need to make a connection with the database, get everything out of it, and turn it into an R-object (tibble/dataframe).

```{r}
db <- odb.open("ideophone.odb")
#db
#names <- names(odb.tables(db))
#tables <- odb.tables(db)
#names
#tables
SQL <- 'SELECT * FROM "ideophone"' #use single and double quotes, quotes around table name
database <- odb.read(db, SQL)
#print(database)
database
```

We are leaving out:
- Zdic
- Ricci
- same_as_ID
- form_letterID
- form_mechanismID


```{r}
#colnames(database)

DBwr <- database %>%
  select(pinyin, pinyintone, traditional, simplified, MC, OC, Kroll, note)
DBwr
```

# Kroll A-M

## Getting R-object

```{r}
Kroll_ar <- readxl::read_excel("kroll_Arthur.xlsx")
Kroll_ar

colnames(Kroll_ar)

KAwr <- Kroll_ar %>%
  rename(traditional = `Kroll Binome`,
         pinyinnum = pinyin,
         Kroll = English,
         notes = Notes,
         radsup = `Radical Support`) %>%
  select(traditional,
         pinyinnum,
         MC,
         Kroll,
         `Morphological Structure`,
         radsup,
         notes)
KAwr
```


# Kroll N-Z

## Getting R-object
```{r}
Kroll_th <- readxl::read_excel("kroll_Thomas.xlsx")
Kroll_th

colnames(Kroll_th)

KTwr <- Kroll_th %>%
  rename(traditional = `Kroll Binome`,
         pinyinnum = pinyin,
         Kroll = English,
         notes = Notes,
         radsup = `Radical Support`) %>%
  select(traditional,
         pinyinnum,
         MC,
         Kroll,
         `Morphological Structure`,
         radsup,
         notes)
KTwr
```

This leaves out:
- page no
- variant

# Combining the tables

```{r}
#DBh <- head(DBwr)
#KTh <- head(KTwr)
#KAh <- head(KAwr)

#colnames(DBh)
#colnames(KTh)
#colnames(KAh)
```

```{r}
joined1 <- full_join(DBwr, KTwr, by = c("traditional", "Kroll", "MC", "note" = "notes"))
joined <- full_join(joined1, KAwr, by = c("traditional", "Kroll", "MC", "note" = "notes", "pinyinnum", "radsup", "Morphological Structure"))
joined
```

# Revamping stuff

## Simplified

Obviously, there are going to be mistakes here.
```{r}
# from trad to simpl
joined <- joined %>%
  mutate(simplified = toTrad(traditional, rev=TRUE)) 
```

## Pinyins
After some testing, it seemed that neither `pinyin` or `tmcn` could bring what I wanted: pinyin without tones, pinyin with tone, pinyin with tone numbers. Thus we need to do this manually?
It seems python can come to the rescue.

Maybe if we split the characters and then combine them again?

```{r}
list <- joined %>%
  select(traditional) %>%
  unlist()
```

```{r}
library(reticulate)
use_python("/usr/local/bin/python3", required = T)
reticulate::py_config()
```

```{python}
import pinyin
a = r.list

thomas = []
for i in a:
    j = pinyin.get(i, delimiter="~")
    thomas.append(j)
    
cj = []
for i in a:
    j = pinyin.get(i, format= "strip", delimiter="~")
    cj.append(j)
    
arthur = []
for i in a:
    j = pinyin.get(i, format="numerical", delimiter="~")
    arthur.append(j)
#print (thomas)
#print(type(thomas))
```

```{r}
#py_run_file("script.py")
#py_run_string("x = 10")

# access the python main module via the 'py' object
#py$x
thomas <- py$thomas #%>% tibble()
thomas <- tibble(thomas)

cj <- py$cj #%>% tibble()
cj <- tibble(cj)

arthur <- py$arthur #%>% tibble()
arthur <- tibble(arthur)

thomas
cj
arthur
```

#



# Distinct entries

```{r}
joined %>%
  distinct()

unique(joined$`Morphological Structure`)

joined %>%
  filter(`Morphological Structure` == "NOTIDEOPHONE")
```















