---
title: "Let’s build a database"
author: "Thomas Van Hoey"
date: "19/9/2018"
html_document:
    toc: TRUE
    theme: united
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goals
What I want to do is combine three documents together:
1. My own database project (.odb)
2. Kroll's (2015) A-M (by Arthur)
3. Kroll's (2015) N-Z (by Thomas)

# Before programming intervenes

* Add 'neglected' entries from dictionary (seems okay)
* Make sure source files are correct (first skype) (okay)
* if both are bn --> RR (seems okay for now)


# Package load
```{r}
library(tidyverse)
library(ODB)
library(tmcn)
library(pinyin)
```


# The .odb database

## Getting the R-object and wrangling

First we need to make a connection with the database, get everything out of it, and turn it into an R-object (tibble/dataframe).

```{r ideodb, cache=TRUE}
db <- odb.open("ideophone.odb")
#db
#names <- names(odb.tables(db))
#tables <- odb.tables(db)
#names
#tables
SQL <- 'SELECT * FROM "ideophone"' #use single and double quotes, quotes around table name
database <- odb.read(db, SQL)
#print(database)
head(database)
```

```{r filterdb}
#database %>%
#  filter(is.na(same_as_ID) == F)
```


We are leaving out:
- Zdic
- Ricci
- same_as_ID
- form_letterID
- form_mechanismID


```{r dbselection}
#colnames(database)

DBwr <- database %>%
  select(pinyin, pinyintone, traditional, simplified, MC, OC, Kroll, note)
#DBwr
```

# Kroll A-M

## Getting R-object

```{r Krollar, cache=TRUE}
Kroll_ar <- readxl::read_excel("kroll_Arthur.xlsx")
#Kroll_ar

#colnames(Kroll_ar)

KAwr <- Kroll_ar %>%
  rename(traditional = `Kroll Binome`,
         pinyinnum = pinyin,
         Kroll = English,
         notes = Notes,
         radsup = `Radical Support`,
         variant = Variant) %>%
  select(traditional,
         pinyinnum,
         MC,
         Kroll,
         `Morphological Structure`,
         radsup,
         variant,
         notes)
head(KAwr)
```


# Kroll N-Z

## Getting R-object
```{r Krollth, cache=TRUE}
Kroll_th <- readxl::read_excel("kroll_Thomas.xlsx")
#Kroll_th

#colnames(Kroll_th)

KTwr <- Kroll_th %>%
  rename(traditional = `Kroll Binome`,
         pinyinnum = pinyin,
         Kroll = English,
         notes = Notes,
         radsup = `Radical Support`,
         variant = Variant) %>%
  select(traditional,
         pinyinnum,
         MC,
         Kroll,
         `Morphological Structure`,
         radsup,
         variant,
         notes)
head(KTwr)
```

This leaves out:
- page no

# Combining the tables

```{r testcombination}
#DBh <- head(DBwr)
#KTh <- head(KTwr)
#KAh <- head(KAwr)

#colnames(DBh)
#colnames(KTh)
#colnames(KAh)
```

```{r joiningtables, cache=TRUE}
joined1 <- full_join(DBwr, KTwr, by = c("traditional", "Kroll", "MC", "note" = "notes"))
joined <- full_join(joined1, KAwr, by = c("traditional", "Kroll", "MC", "note" = "notes", "pinyinnum", "radsup", "Morphological Structure", "variant" = "variant"))
head(joined)
```

# Revamping stuff

## Simplified

Obviously, there are going to be mistakes here.
```{r simplified, cache=TRUE}
# from trad to simpl
joined <- joined %>%
  mutate(simplified = toTrad(traditional, rev=TRUE)) 
```

## Pinyin

After some testing, it seemed that neither `pinyin` or `tmcn` could bring what I wanted: pinyin without tones, pinyin with tone, pinyin with tone numbers. Thus we need to do this manually?
It seems python can come to the rescue.

```{r unlisting}
list <- joined %>%
  select(traditional) %>%
  unlist()
```

```{r pythonreticulate}
library(reticulate)
use_python("/usr/local/bin/python3", required = T)
reticulate::py_config()
```

```{python pyscript}
import pinyin
a = r.list

richard = []
for i in a:
    richard.append(i)

thomas = []
for i in a:
    j = pinyin.get(i, delimiter="~")
    thomas.append(j)
    
cj = []
for i in a:
    j = pinyin.get(i, format= "strip", delimiter="~")
    cj.append(j)
    
arthur = []
for i in a:
    j = pinyin.get(i, format="numerical", delimiter="~")
    arthur.append(j)
#print (thomas)
#print(type(thomas))
```

```{r pythonvars}
#py_run_file("script.py")
#py_run_string("x = 10")

# access the python main module via the 'py' object
#py$x
thomas <- py$thomas #%>% tibble()
thomas <- tibble(thomas)

cj <- py$cj #%>% tibble()
cj <- tibble(cj)

arthur <- py$arthur #%>% tibble()
arthur <- tibble(arthur)

#thomas
#cj
#arthur
```

```{r joiningnewpinyin, cache=TRUE}
joined <- cbind(joined, arthur, thomas, cj)
head(joined)
```




# zdic entries

## set up
```{r}
library(rvest)
```

```{r opzoeken.function, cache=TRUE}
opzoeken <- function(query){
  
  Sys.sleep(1)
  
  # Specify URL
  url <- "http://wap.zdic.net/"
  session <- html_session(url)

  # Grab Initial Form
  #  Form is filled in stages. Here, only do country and date
  form.unfilled <- 
    session %>% 
    html_node("form") %>% 
    html_form()

  form.filled <- 
    form.unfilled %>%
    set_values("q" = query)

  # submit the form and save as a new session
  submitted <- submit_form(session, form.filled) 

  # look for a definition in the nodes
  definitie <- 
    submitted %>% 
    html_nodes(xpath = "/html/body/div/div[1]/div/ol/div/li/p[1]") %>%
    html_text()
  
  if (is_empty(definitie) == TRUE){
    definitie <- "NA"
  } else {
    definitie <- definitie
  }

  pronunciation <-
    submitted %>%
    html_nodes(xpath = "//rtc//rt") %>%
    html_text()

  pinyin <- pronunciation[1]
  zhuyin <- pronunciation[2]

  df <- data.frame(
    woord = query,
    pinyin = pinyin,
    zhuyin = zhuyin,
    definitie = definitie %>%
      paste(collapse = "")
  )
  write_csv(df, "meanings.csv", append = TRUE)
}

opzoeken <- possibly(opzoeken, otherwise = NA_real_)
```


With the head() this worked, so probably with all the rest too.
(I am turning this off because it takes 40 minutes to run)
```{r runlookup, cache=TRUE}
#list2 <- py$richard #%>% head()
#map_df(list2, opzoeken) %>%
#  select(woord, definitie)
```

Finished running!
Saved as "meanings.csv".

# Finishing touches
## Put all extra tables together
```{r zdic, cache=TRUE}
zdictable <- read_csv("meanings.csv", col_names = F)
handian <- zdictable %>%
  rename(zhuyin = X3, zdic = X4) %>%
  select(zhuyin, zdic)
zhuyin <- handian$zhuyin
zdic <- handian$zdic

final <- cbind(joined, zhuyin, zdic)
```

## Sort the final table + sort the variables
```{r combined, cache=TRUE}
final <- final %>%
  arrange(cj) %>%
  rename(morphology = `Morphological Structure`)

#colnames(final)

final <- final[c("pinyin", "pinyintone", "pinyinnum",
        "arthur", "thomas", "cj",
        "traditional", "simplified",
        "MC", "OC", 
        "morphology", "radsup",
        "variant",
        "Kroll", "zdic", "note")]
head(final) 
```

## Write the table
```{r}
#write_csv(final, "combined_table.csv")
```



# Stuff that needs to happen after coding.

## Higher priorities

* Manually checking all three new pronunciations agains the old ones. The old ones were only partially filled out, but they were correct. With computing it is possible to fill out the whole table but it might be wrong. (ok)
* Checking traditional vs. simplified characters. (ok)
* add pinyin with tones based on numbers (ok)

* Fill out MC
* Fill out OC

```{r baxter1, cache=TRUE}
# read in file
updated <- read_csv("combined_manualcheck.csv") 
update <- updated%>%
  mutate(id = rownames(updated))

split_trad <- updated %>%
  mutate(first = str_extract(traditional, "^."),
         second = str_extract(traditional, ".$"))
#split_trad

baxter <- readxl::read_excel("../BaxterSagartOC2015-10-13.xlsx") 
head(baxter)
```
Combining the two datasets
```{r baxter2, cache=TRUE}
baxter2 <- baxter %>%
  rename("middle" = "MC", "old" = "OC") %>%
  select(zi, middle, old)

test <- split_trad %>% dplyr::left_join(dplyr::distinct(baxter2, zi,
                                                          .keep_all = T),
                                          by = c("first" = "zi")) %>%
  rename("mid1" = "middle",
         "old1" = "old") %>%
  dplyr::left_join(dplyr::distinct(baxter2, zi, .keep_all = T),
                                by = c("second" = "zi")) %>%
  rename("mid2" = "middle",
         "old2" = "old") %>%
  unite(mid1, mid2, col = "Bmid", sep = "~") %>%
  unite(old1, old2, col = "Bold", sep = "~") %>%
  select(-c(first, second, OC))
head(test)
```


```{r}
#write_csv(test, "combined_baxter.csv")
```

* Fill out radsup (ok)
* add pinyin wihtout anything based on numbers (ok)
* Fill out reduplication pattern (BR RED RB ...) (coding ok)

```{r morph, cache=TRUE}
radsup <- read_csv("combined_radsup.csv")
#radsup
morph <- radsup %>%
  mutate(first = str_extract(traditional, "^."),
         second = str_extract(traditional, ".$")) %>%
  mutate(morph = case_when(first == second ~ "RED",
                            morphology == "RED" ~ "RED",
                            morphology == "BR" ~ "BR",
                            morphology == "RB" ~ "RB",
                            morphology == "RR" ~ "RR",
                            morphology == "SINGLE" ~ "SINGLE",
                            morphology == "NOTIDEOPHONE" ~ "NOTIDEOPHONE",
                            morphology == "RAN" ~ "RAN",
                            morphology == "YAN" ~ "YAN",
                            morphology == "NA" ~ "NA")) %>%
  mutate(MC2 = str_replace(MC, "-", "~")) %>%
  mutate(MC2 = str_replace(MC2, " ", "~")) %>%
  select(-MC) %>%
  rename(pinyinnum = arthur,
         pinyintone = thomas,
         MC = MC2) %>%
  mutate(pinyinnone = str_replace_all(pinyinnum, "\\d", "")) %>%
  select(pinyinnum, pinyintone, pinyinnone,
         traditional, simplified,
         MC, OC,
         radsup, morph, 
         variant,
         Kroll, zdic,
         note)


head(morph)

#write_csv(morph, "combined_morph.csv")
```

* The ones that were coded with RAN should (technically) be recoded -ran
, so check coding of reduplication (with ~/-) (is ok because we have morph column)
* Fill out reduplication pattern (BR RED RB ...) (needs manual)



# Things that we can still do, but are not super necessary at the moment


* making some extra columns with more pinyin (without segmenter ~/-)
* Variation of 山 radical 
* calculate chance of radical support




