---
title: "mao"
author: "Thomas Van Hoey"
date: "20-5-2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Mao 貌 as a predictor for ideophones

The idea is that *mao* 貌 can focus as a predictor in dictionary definitions.
Let's calculate the stats in CHIDEOD.

```{r}
library(CHIDEOR)
library(tidyverse)
```

Loading the tidy hydcd
```{r}
tidy.hydcd <- read_rds("/Users/Thomas/Google\ Drive/hydcd/tidyHYDCD.rds")
```


```{r}
db <- full_database

# select relevant columns and left join
db_hydcd <- db %>% 
  select(traditional) %>%
  left_join(tidy.hydcd, by = c("traditional" = "item")) %>%
  select(-computemeaning)

# only numbered meanings, examples gone
db_hydcd %>%
  filter(str_detect(printmeaning, "^[:digit:]")) %>%
  separate(printmeaning, into = c("meaning", "example"), sep = "\n") %>%
  distinct() -> db_tidy
```





How many have the marker mao in their definition?
```{r}
distincts <- db_tidy %>%
  distinct(traditional) 

distinctsmao <- db_tidy %>%
  filter(str_detect(meaning, "貌")) %>%
  distinct(traditional) 

distinctssheng <- db_tidy %>%
  filter(str_detect(meaning, "聲")) %>%
  distinct(traditional) 

# numbers
nrow(distincts)
nrow(distinctsmao)
nrow(distinctssheng)

# overlap

#intersect(distinctsmao, distinctssheng)
intersect(distinctsmao, distinctssheng) %>% nrow()
```

So we can see that there are `nrow(distincts)` distinct ideophones in CHIDEOD that have a definition in HYDCD.
Of these `nrow(distinctsmao)` have *mao* 貌 as a marker; and `nrow(distinctssheng)` *sheng* 聲 as a marker.
There is some overlap, namely n = `intersect(distinctsmao, distinctssheng) %>% nrow()`. 

This means that *mao* is a pretty good marker for ideophones: `nrow(distinctsmao) / nrow(distincts)`.

# Mao for finding new possible ideophones

So let's say we have *mao*, let's look in HYDCD at all the definitions that have this marker, in a somewhat onomasiological fashion.

```{r}
hydcd_split <- tidy.hydcd %>%
  select(-computemeaning) %>%
  filter(str_detect(printmeaning, "^[:digit:]")) %>%
  separate(printmeaning, into = c("meaning", "example"), sep = "\n") %>%
  distinct() 

hydcd_mao <- hydcd_split %>%
  filter(str_detect(meaning, "貌。")) # add period

hydcd_sheng <- hydcd_split %>%
  filter(str_detect(meaning, "聲。")) # add period

```

Which ones **do not** occur in CHIDEOD?
```{r}
hydcd_mao %>%
  anti_join(distinctsmao, by = c("item" = "traditional")) %>%
  group_by(item) %>%
  mutate(meaning = paste(meaning, collapse = "; "),
         example = paste(example, collapse = "; ")) %>%
  distinct() -> hydcd_mao2


hydcd_sheng %>%
  anti_join(distinctsmao, by = c("item" = "traditional")) %>%
  group_by(item) %>%
  mutate(meaning = paste(meaning, collapse = "; "),
         example = paste(example, collapse = "; ")) %>%
  distinct() -> hydcd_sheng2

#hydcd_mao2
#hydcd_sheng2
```

Numbers of groups.
```{r}
hydcd_sheng %>%
  distinct(item)

hydcd_sheng2 %>%
  distinct(item)


hydcd_mao %>%
  distinct(item)

hydcd_mao2 %>%
  distinct(item)
``` 


These results can now be further examined in a spreadsheet.
They are possible candidates

```{r}
# write_csv(hydcd_mao2, "hydcd_mao.csv", col_names = TRUE)
# write_csv(hydcd_sheng2, "hydcd_sheng.csv", col_names = TRUE)
```

---

# Other definitional lexical predictors?

Perhaps CHIDEOD harbours other lexical predictors in its definitions?

```{r}
library(tidytext)

db_tidy %>%
  unnest_tokens(input = meaning, 
                token = "characters",
                output = "chars",
                drop = FALSE) %>%
  select(chars) %>%
  count(chars) %>%
  filter(! str_detect(chars, "[:digit:]")) %>%
  arrange(desc(n)) %>%
  head(20)

```


As can be seen, there are 1735 *mao*s in the definition, and 864 *sheng*s. So they are probably good predictors.
So this is further evidence that they are probably structural, closed-class used.
However, there are no other predictors (maybe '象聲詞'?). 

Will bigrams bring solace?
```{r}
db_tidy %>%
  mutate(meaning = str_replace_all(meaning, "(.{1})", "\\1 ")) %>%
  unnest_tokens(input = meaning, 
                token = "ngrams",
                n = 2,
                output = "chars",
                drop = FALSE) %>%
  select(chars) %>%
  filter(! str_detect(chars, "[:digit:]")) %>%
  count(chars, sort = TRUE) %>%
   head(20)
```


---

# First treatment (after first manual checking, n = 500)

```{r}
first <- read_csv("hydcd_mao.csv")
first %>%
  mutate(n = nchar(item),
         ch1 = str_extract(item, "^."),
         ch2 = str_extract(item, ".$")) %>%
  select(n, everything()) %>%
  mutate(type = case_when(
  n == "1" ~ "e",
  type == "Q" ~ "q",
  is.na(type) == FALSE ~ type,
  str_detect(item, "然") ~ "ideo",
  ch1 == ch2 & n == 2 ~ "ideo",
  n == 4 ~ "prov"
  )) %>%
  arrange(type)  -> maofirst
  
#write_csv(maofirst, "maofirst.csv", col_names = TRUE)
```

```{r}
first_sheng <- read_csv("hydcd_sheng.csv")
first_sheng %>%
  mutate(type = "NA",
         n = nchar(item),
         ch1 = str_extract(item, "^."),
         ch2 = str_extract(item, ".$")) %>%
  mutate(type = case_when(str_detect(meaning, "之聲") ~ "ideo",  
                          str_detect(meaning, "象聲詞") ~ "ideo",
                          str_detect(meaning, "叫聲") ~ "ideo", 
                          str_detect(meaning, "鳴聲") ~ "ideo", 
                          str_detect(meaning, "笑聲") ~ "ideo", 
                          str_detect(meaning, "形容") ~ "ideo", 
                          #n == "1" ~ "e",
                          #type == "Q" ~ "q",
                          is.na(type) == FALSE ~ type,
                          #str_detect(item, "然") ~ "ideo",
                          ch1 == ch2 & n == 2 ~ "ideo",
                          n == 4 ~ "prov"
  )) %>%
  select(n, type, everything()) %>%
  arrange(type) -> shengfirst
  
#write_csv(shengfirst, "shengfirst.csv", col_names = TRUE)
```

```{r}
second_sheng <- read_csv("shengfirst.csv")
second_sheng %>%
  mutate(type = case_when(
    is.na(type) == FALSE ~ type,
    str_detect(meaning, "名聲") ~ "not",
    str_detect(meaning, "比喻") ~ "not",
  )) %>%
  arrange(type) -> shengsecond

#write_csv(shengsecond, "shengsecond.csv", col_names = TRUE)
```

---

```{r}
sheng_analyzed <- read_csv("shengsecond.csv") %>%
  mutate(type = as_factor(type))



mao_analyzed <- read_csv("maofirst.csv") %>%
  mutate(type = case_when(
    type == "prov" ~ "phrase",
    type == "saying" ~ "phrase",
    type == "e" ~ "single",
    type == "q" ~ "possible candidate",
    TRUE ~ type
  ),
  type = as_factor(type))

#ggplots
mao_groups <- mao_analyzed %>%
  count(type) %>%
  ggplot(aes(x = reorder(type, n), y = n)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_classic() +
  ylab("frequency of mao") +
  xlab("")


sheng_groups <- sheng_analyzed %>%
  count(type) %>%
  ggplot(aes(x = reorder(type, n), y = n)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_classic() +
  ylab("frequency of sheng") +
  xlab("")
``` 

---

```{r}
tidy.hydcd %>%
  filter(item == "貌")
```








