---
title: "tidyhanchi_diachronic"
author: "Thomas Van Hoey"
date: "10/23/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
start_time <- Sys.time()
```


# Setting up
## Packages
```{r}
library(tidyverse)
library(tidytext)
library(widyr)
library(plotly)
```


## Function definitions

### `slide_windows`
```{r}
slide_windows <- function(tbl, doc_var, window_size) {
    # each word gets a skipgram (window_size words) starting on the first
    # e.g. skipgram 1 starts on word 1, skipgram 2 starts on word 2
    
    each_total <- tbl %>% 
        group_by(!!doc_var) %>% 
        mutate(doc_total = n(),
               each_total = pmin(doc_total, window_size, na.rm = TRUE)) %>%
        pull(each_total)
    
    rle_each <- rle(each_total)
    counts <- rle_each[["lengths"]]
    counts[rle_each$values != window_size] <- 1
    
    # each word get a skipgram window, starting on the first
    # account for documents shorter than window
    id_counts <- rep(rle_each$values, counts)
    window_id <- rep(seq_along(id_counts), id_counts)

    
    # within each skipgram, there are window_size many offsets
    indexer <- (seq_along(rle_each[["values"]]) - 1) %>%
        map2(rle_each[["values"]] - 1,
             ~ seq.int(.x, .x + .y)) %>% 
        map2(counts, ~ rep(.x, .y)) %>%
        flatten_int() +
        window_id
    
    tbl[indexer, ] %>%
        bind_cols(data_frame(window_id)) %>%
        group_by(window_id) %>%
        filter(n_distinct(!!doc_var) == 1) %>%
        ungroup
}
```


### `tidy_pmi`
```{r}
tidy_pmi <- function(dataframe){
  dataframe %>%
    unnest_tokens(word, text, token = "regex", pattern = " ") %>%
    add_count(word) %>%
    filter(n >= 5) %>% 
    select(-n) %>%
    slide_windows(quo(postID), 8) %>%
    pairwise_pmi(word, window_id)
}
```

### `checking_tidy_pmi `
This is a heuristic function if something goes wrong.
```{r}
checking_tidy_pmi <- function(tidydataframe, column, target){
  tidydataframe %>%
    filter(column %in% target) #target needs to be character
}
```

### `tidy_word_vectors`
```{r}
tidy_word_vectors <- function(tidydataframe){
  tidydataframe %>%
    widely_svd(item1, item2, pmi, nv = 256, maxit = 1000)
}
```

### `nearest_synonyms`
```{r}
nearest_synonyms <- function(df, token) {
    df %>%
    widely(~ . %*% (.[token, ]), 
           sort = TRUE)(item1, dimension, value) %>%
    select(-item2)
}
```

### `result_table`
```{r}
resulttable <- function(textobject){
  
  TARGETbare <- textobject %>%
    str_extract(".._") %>%
    str_remove("_")    
  
  suffix <- str_extract(textobject, "_[a-z]*")
  
  text_df <- textobject %>% 
    read_lines() %>%
    unlist() %>%
    data_frame(text = .) %>%
    distinct() %>% 
    mutate(postID = row_number())
  
  results <- text_df %>%
    tidy_pmi() %>%
    tidy_word_vectors() %>%
    nearest_synonyms(TARGETbare) %>%
    top_n(1000)
  
  path <- sprintf("./diachronic/%s%s.csv", TARGETbare, suffix)
  
  if (!file.exists(path)){
    dir.create("./diachronic")
    file.create(path)
  }
  
  write_csv(results, path, append = F)
}
```

```{r}
files[1] %>%
  str_extract(".._") %>%
  str_remove("_")
```

# Data read in

Variables
```{r}
TARGETbare <- "灼灼"
TARGET <- sprintf("%s_.*", TARGETbare)
```

File locations
```{r}
files <- list.files(path = "./segmented", 
                    pattern = sprintf('%s.*.txt', TARGET), 
                    full.names = TRUE)
files
```


# Function call
```{r}
map(files, resulttable)
#results
```

This is to where this script / document should be run first.


Benchmark
```{r}
end_time <- Sys.time()
end_time - start_time
```




# Analysis time

```{r}
dia_files <- list.files(path = "./diachronic", 
                        pattern = sprintf('%s.*.csv', TARGETbare), 
                        full.names = TRUE)
dia_files
```

sprintf("./diachronic/%s_xianqin.csv", TARGETbare)
```{r}
xianqin <- read_csv(sprintf("./diachronic/%s_xianqin.csv", TARGETbare)) %>%
  rename(xianqin = value)
qinhan <- read_csv(sprintf("./diachronic/%s_qinhan.csv", TARGETbare)) %>%
  rename(qinhan = value)
weijin <- read_csv(sprintf("./diachronic/%s_weijin.csv", TARGETbare)) %>%
  rename(weijin = value)
suitang <- read_csv(sprintf("./diachronic/%s_suitang.csv", TARGETbare)) %>%
  rename(suitang = value)
songjin <- read_csv(sprintf("./diachronic/%s_songjin.csv", TARGETbare)) %>%
  rename(songjin = value)
yuan <- read_csv(sprintf("./diachronic/%s_yuan.csv", TARGETbare)) %>%
  rename(yuan = value)
ming <- read_csv(sprintf("./diachronic/%s_ming.csv", TARGETbare)) %>%
  rename(ming = value)
qing <- read_csv(sprintf("./diachronic/%s_qing.csv", TARGETbare)) %>%
  rename(qing = value)
minguo <- read_csv(sprintf("./diachronic/%s_minguo.csv", TARGETbare)) %>%
  rename(minguo = value)
```

```{r}
untidytable <- xianqin %>% 
  full_join(qinhan, by = "item1") %>%
  full_join(weijin, by = "item1") %>%
  full_join(suitang, by = "item1") %>%
  full_join(songjin, by = "item1") %>%
  full_join(yuan, by = "item1") %>%
  full_join(ming, by = "item1") %>%
  full_join(qing, by = "item1") %>%
  full_join(minguo, by = "item1") %>%
  filter(!item1 == TARGETbare) %>%
  filter(!item1 == "之") %>%
  filter(item1 != "，") %>%
  filter(item1 != "。") %>%
  filter(item1 != "曰") %>%
  filter(item1 != "［") %>%
  filter(item1 != "］") %>%
  filter(item1 != " ")
  #slice(-1)
untidytable

#untidytable
#untidytable %>%
#  head(1) %>%
#  select(item1) %>%
#  pull() 

tidytable <- untidytable %>%
  gather(`xianqin`, `qinhan`, `weijin`,
         `suitang`, `songjin`, `yuan`, 
         `ming`, `qing`, `minguo`,
         key = "period", 
         value = "values") %>%
  mutate(ideophone = TARGETbare)
tidytable

tidytable$period <- factor(tidytable$period,
                           levels = c('xianqin', 
                                      'qinhan', 
                                      'weijin',
                                      'suitang', 
                                      'songjin', 
                                      'yuan', 
                                      'ming', 
                                      'qing', 
                                      'minguo'))

tidyplot <- tidytable %>%
  arrange(desc(values)) %>%
  top_n(100) %>%
  ggplot(aes(period, values, label = item1)) + 
  #geom_point() +
  geom_text(family="Noto Sans CJK TC") +
  geom_line(aes(group = item1), linetype = "dotted", color = "grey") +
  theme(text = element_text(family="Noto Sans CJK TC")) 
  
ggplotly(tidyplot)

```


# Onomasiological analysis

```{r}
ONOMA <- c("日","其華") 


tidytable %>%
  filter(item1 == ONOMA) %>%
  ggplot(aes(period, values, label = ideophone)) + 
  geom_point() +
  #geom_text(family="Noto Sans CJK TC") +
  geom_line(aes(group = item1), linetype = "dotted", color = "grey") +
  theme(text = element_text(family="Noto Sans CJK TC")) +
  facet_grid(cols = vars(item1)) +
  ggtitle("Onomasiological studies")
```

Of course this only becomes interesting when we have multiple ideophones to compare this with, but in the same domain!

Path worth exploring.










