---
title: "onomatopoeia_database"
author: "Thomas Van Hoey"
date: "3/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tmcn)
library(reticulate)
library(readxl)
library(xlsx)
```

# Goal columns

## with R
pinyinnum
pinyintone
pinyinnone
traditional
simplified
middlechinese MC (not super relevant, but still try to)
oldchinese OC (not super relevant, but still try to)
datasource
sensory_modality ('SOUND')

## manually

variants
check for pinyin errors

# Datasources

There are three

* "LiJingEr"
* "GongLiangYu"
* "WangWanRen"


Read in
```{r}
name <- "LiJingEr"
file <- read_lines(sprintf("%s.txt", name)) %>%
  as.tibble() %>%
  rename(onom = value)
file
```

## add pinyin with python

load in
```{r pythonreticulate}
use_python("/usr/local/bin/python3", required = T)
reticulate::py_config()
```

get only the characters from our list
```{r unlisting}
list <- file %>%
  select(onom) %>%
  unlist()
```


```{python pyscript}
import pinyin
a = r.list

richard = []
for i in a:
    richard.append(i)

thomas = []
for i in a:
    j = pinyin.get(i, delimiter="~")
    thomas.append(j)
    
cj = []
for i in a:
    j = pinyin.get(i, format= "strip", delimiter="~")
    cj.append(j)
    
arthur = []
for i in a:
    j = pinyin.get(i, format="numerical", delimiter="~")
    arthur.append(j)
#print (thomas)
#print(type(thomas))
```

```{r pythonvars}
#py_run_file("script.py")
#py_run_string("x = 10")

# access the python main module via the 'py' object
#py$x
thomas <- py$thomas #%>% tibble()
thomas <- tibble(thomas)

cj <- py$cj #%>% tibble()
cj <- tibble(cj)

arthur <- py$arthur #%>% tibble()
arthur <- tibble(arthur)

#thomas
#cj
#arthur
```

```{r joiningnewpinyin, cache=TRUE}
joined <- cbind(file, arthur, thomas, cj) %>%
  rename(pinyinnum = arthur,
         pinyintone = thomas,
         pinyinnone = cj, 
         traditional  = onom)
head(joined)
joined
```

## Add simplified

```{r}
tradsimp <- joined %>% 
  mutate(simplified = toTrad(traditional, rev = TRUE))
```

## Add middle and old chinese

```{r}
splitcharacters <- tradsimp %>%
  mutate(c1 = str_extract(traditional, "^."),
         c2 = str_extract(traditional, "^.."),
         c3 = str_extract(traditional, "^..."),
         c4 = str_extract(traditional, "^...."),
         c5 = str_extract(traditional, "^....."),
         c6 = str_extract(traditional, "^......"),
         c7 = str_extract(traditional, "^.......")
         ) %>%
  mutate(c2 = str_replace(c2, "^.", ""),
         c3 = str_replace(c3, "^..", ""),
         c4 = str_replace(c4, "^...", ""),
         c5 = str_replace(c5, "^....", ""),
         c6 = str_replace(c6, "^.....", ""),
         c7 = str_replace(c7, "^......", ""))
splitcharacters
```

load in Baxter Sagart

```{r}
baxter <- readxl::read_excel("../BaxterSagartOC2015-10-13.xlsx") %>%
  rename("middle" = "MC", "old" = "OC") %>%
  select(zi, middle, old)
head(baxter)
```

```{r}
midandoldpercharacter <- splitcharacters %>% 
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c1"= "zi")) %>%
  rename("m1" = "middle",
         "o1" = "old") %>% # this lef_join and rename function gets repeated but the number is changed
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c2"= "zi")) %>%
  rename("m2" = "middle",
         "o2" = "old") %>%
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c3"= "zi")) %>%
  rename("m3" = "middle",
         "o3" = "old") %>%
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c4"= "zi")) %>%
  rename("m4" = "middle",
         "o4" = "old") %>%
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c5"= "zi")) %>%
  rename("m5" = "middle",
         "o5" = "old") %>%
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c6"= "zi")) %>%
  rename("m6" = "middle",
         "o6" = "old") %>%
  dplyr::left_join(dplyr::distinct(baxter,
                                   zi,
                                   .keep_all = T),
                   by = c("c7"= "zi")) %>%
  rename("m7" = "middle",
         "o7" = "old")  

# combinations
nummers <- 1:7
middles <- paste0("m", nummers)
olds <- paste0("o", nummers)

midold <- midandoldpercharacter %>%
  unite(middles, col = "MC", sep = "~") %>%
  unite(olds, col = "OC", sep = "~") %>%
  mutate(OC = str_replace(OC, "NA~NA~NA~NA~NA~NA~NA", "NA"),
         OC = str_replace(OC, "NA~NA~NA~NA~NA~NA", "NA"),
         OC = str_replace(OC, "NA~NA~NA~NA~NA", "NA"),
         OC = str_replace(OC, "NA~NA~NA~NA", "NA"),
         OC = str_replace(OC, "NA~NA~NA", "NA"),
         OC = str_replace(OC, "~NA$", ""),
         MC = str_replace(MC, "NA~NA~NA~NA~NA~NA~NA", "NA"),
         MC = str_replace(MC, "NA~NA~NA~NA~NA~NA", "NA"),
         MC = str_replace(MC, "NA~NA~NA~NA~NA", "NA"),
         MC = str_replace(MC, "NA~NA~NA~NA", "NA"),
         MC = str_replace(MC, "NA~NA~NA", "NA"),
         MC = str_replace(MC, "~NA$", "")
         )
```

## Data source and sensory modality

```{r}
arrangeddb <- midold %>%
  mutate(datasource = name,
         sensorymod = "SOUND") %>%
  select(pinyintone,
         pinyinnone,
         pinyinnum,
         traditional,
         simplified,
         MC,
         OC,
         datasource,
         sensorymod)
```

# Write into new csv file

```{r}
write_csv(arrangeddb, sprintf("%s.csv", name), col_names = TRUE)
write.xlsx(arrangeddb, sprintf("%s.xlsx", name), col.names = TRUE)

```

# After manually checking

Read in checked files

```{r}
li <- read_excel("LiJingEr_checked.xlsx") #%>% select(`..1`)
wang <- read_csv("WangWanRen_checked.csv")
gong <- read_csv("GongLiangYu_checked.csv")
wang
gong
li
```

```{r}
onom <- full_join(wang, gong) %>%
  full_join(li) %>%
  mutate(datasource = case_when(
    datasource == "WangWanRen" ~ "Wang",
    datasource == "GongLiangYu" ~ "Gong",
    datasource == "LiJingEr" ~ "Li"
    )) %>%
  mutate(pinyinnone = str_replace_all(pinyinnum, "[12345]", ""))
onom

write_csv(onom, "onomatopoeiadb.csv", col_names = TRUE)

onom %>%
  group_by(datasource) %>%
  tally()

```

```{r}
onom %>%
  distinct(traditional) %>%
  mutate(syllength = nchar(traditional)) %>%
  group_by(syllength) %>%
  tally() %>%
  filter(syllength != 5 & syllength !=6) %>%
  mutate(expected = sum(n)/4) %>%
  ungroup() %>%
  summarise(pval = chisq.test(n, syllength)$p.value)
```

```{r}
test <- onom %>%
  distinct(traditional) %>%
  mutate(syllength = nchar(traditional)) %>%
  group_by(syllength) %>%
  tally() %>%
  filter(syllength != 5 & syllength !=6) %>%
  group_by(syllength, n) %>%
  summarise(
    count = n(),
    mean = mean(n, na.rm = TRUE),
    sd = sd(n, na.rm = TRUE)
  )

  res.aov <- aov(n ~ syllength, data = test)
  res.aov
```



